---
title: "MultimodalAnalysis_ADdatasets"
author: "DG"
date: "2026-04-17"
output: html_document
---
MULTIMODAL ANALYSIS

Proteomics (Unwin group datasets)
•	EC dataset (AD vs control, 9 samples per group) 
•	HIP dataset (AD vs control, 6 samples per group) 
•	IDs = UniProt 
•	Working ID = SYMBOL 

RNA microarray 
•	GSE5281 dataset (AD vs control)
•	Multiple brain regions(EC, HIP, MTG, PC, SFG, VCX)
•	IDs = PROBEID (Affymetrix)
•	Utilised EC and HIP datasets to match proteomic data
•	Working ID = SYMBOL 

“Gene symbols were used as a common identifier, acknowledging potential ambiguity due to gene name aliases.”
---
## 1. Convert both datasets to common IDs
library(org.Hs.eg.db)

library(clusterProfiler)

library(dplyr)

##Read datasets
ec_map <- bitr(ec_sig$protein,
               fromType = "UNIPROT",
               toType   = "SYMBOL",
               OrgDb    = org.Hs.eg.db)

hip_map <- bitr(hip_sig$protein,
                fromType = "UNIPROT",
                toType   = "SYMBOL",
                OrgDb    = org.Hs.eg.db)

rna_ec <- read.csv("limma_EC_annotated.csv")

rna_hip <- read.csv("limma_HIP_annotated.csv")

## Study column format 
colnames(ec_sig)

colnames(ec_map)

colnames(hip_sig)

colnames(hip_map)

## Convert to ubiquitous format
#EC dataset
colnames(ec_sig)[colnames(ec_sig) == "uniprot"] <- "UNIPROT"

ec_merged <- merge(ec_sig, ec_map, by = "UNIPROT")

ec_merged %>%
+     group_by(SYMBOL) %>%
+     summarise(logFC = mean(logFC), .groups = "drop")

ec_multi <- inner_join(ec_merged, rna_ec, by = "SYMBOL")

#HIP dataset
colnames(hip_sig)[colnames(hip_sig) == "uniprot"] <- "UNIPROT"

hip_merged <- merge(hip_sig, hip_map, by = "UNIPROT")

hip_merged %>%
+     group_by(SYMBOL) %>%
+     summarise(logFC = mean(logFC), .groups = "drop")

hip_multi <- inner_join(hip_merged, rna_hip, by = "SYMBOL")

## QC check - ensure proper database formation
nrow(ec_multi)

nrow(hip_multi)

# result 
nrow(ec_multi)
#[1] 0
nrow(hip_multi)
#[1] 0

# This means that merging failed totally and needs to be re-done (probably due to naming differences, e.g. tp53, Tp53, TP53)

## Start merging again

#Inspect both SYMBOL columns
head(ec_merged$SYMBOL)

head(rna_ec$SYMBOL)

rownames(ec_sig)[1:10]
#[1] "1"  "2"  "3"  "4"  "5"  "6"  "7"  "8"  "9"  "10"

colnames(ec_sig)

#[1] "UNIPROT"     "LOGFC"       "AVEEXPR"     "T"           "P.VALUE"    
#[6] "ADJ.P.VAL"   "B"           "SIGNIFICANT" "CATEGORY"

rownames(hip_sig)[1:10]

colnames(hip_sig)

#Use correct column name

ec_ids <- ec_sig$UNIPROT
hip_ids <- hip_sig$UNIPROT

#QC check IDs

head(ec_ids)

# outputs is this: [1] "Q96EQ0" "P02743" "P27338" "P17302" "Q13228" "P02763", which is perfect

head(hip_ids)

#Mapping

library(clusterProfiler)
library(org.Hs.eg.db)

ec_map <- bitr(ec_ids,
               fromType = "UNIPROT",
               toType   = "SYMBOL",
               OrgDb    = org.Hs.eg.db)

library(clusterProfiler)
library(org.Hs.eg.db)

hip_map <- bitr(hip_ids,
               fromType = "UNIPROT",
               toType   = "SYMBOL",
               OrgDb    = org.Hs.eg.db)

#Run QC check

nrow(ec_map)
head(ec_map)

nrow(hip_map)
head(hip_map)

#Step 4 — Merge correctly
ec_merged <- dplyr::inner_join(
  ec_sig,
  ec_map,
  by = c("UNIPROT" = "UNIPROT")
)

hip_merged <- dplyr::inner_join(
  hip_sig,
  hip_map,
  by = c("UNIPROT" = "UNIPROT")
)

#Run QC check
nrow(ec_merged)
head(ec_merged$SYMBOL)

nrow(hip_merged)
head(hip_merged$SYMBOL)

nrow(ec_sig)
#[1] 301
nrow(ec_merged)
#[1] 296
nrow(ec_multi)
#[1] 0

nrow(hip_sig)
#[1] 52
nrow(hip_merged)
#[1] 53
nrow(hip_multi)
#[1] 0

#We get adequate raw DE values and mapping is working, therefore the problem is RNA-protein mapping (SYMBOL mismatch)

## Start merging again 2

# Identify failure point
length(intersect(ec_merged$SYMBOL, rna_ec$SYMBOL))

length(intersect(hip_merged$SYMBOL, rna_hip$SYMBOL))

# Inspect SYMBOL formats in the different files
head(ec_merged$SYMBOL, 20)

head(rna_ec$SYMBOL, 20)

head(hip_merged$SYMBOL, 20)

head(rna_hip$SYMBOL, 20)

# Force standarization (before merging)

ec_merged$SYMBOL <- toupper(trimws(ec_merged$SYMBOL))
rna_ec$SYMBOL    <- toupper(trimws(rna_ec$SYMBOL))

hip_merged$SYMBOL <- toupper(trimws(hip_merged$SYMBOL))
rna_hip$SYMBOL    <- toupper(trimws(rna_hip$SYMBOL))

# Check overlap

length(intersect(ec_merged$SYMBOL, rna_ec$SYMBOL))

length(intersect(hip_merged$SYMBOL, rna_hip$SYMBOL))

# Merging
ec_multi <- dplyr::inner_join(
  ec_merged,
  rna_ec,
  by = "SYMBOL"
)

hip_multi <- dplyr::inner_join(
  hip_merged,
  rna_hip,
  by = "SYMBOL"
)

# Inspect Merging Success
nrow(ec_multi)
head(ec_multi)

nrow(hip_multi)
head(hip_multi)

#Merging and integration worked

## 2. Convert both datasets to common IDs
# 2.1. Inspect column labels

colnames(ec_multi)

# [1] "UNIPROT"     "LOGFC"       "AVEEXPR"     "T"           "P.VALUE"    
# [6] "ADJ.P.VAL"   "B.x"         "SIGNIFICANT" "CATEGORY"    "SYMBOL"     
#[11] "X"           "logFC"       "AveExpr"     "t"           "P.Value"    
#[16] "adj.P.Val"   "B.y"         "ENTREZID"    "GENENAME"  
#Current column label format:
#•	LOGFC → protein logFC 
#•	logFC → RNA logFC

colnames(hip_multi)

# [1] "UNIPROT"     "logFC.x"     "AveExpr.x"   "t.x"         "P.Value.x"  
# [6] "adj.P.Val.x" "B.x"         "significant" "category"    "SYMBOL"     
#[11] "X"           "logFC.y"     "AveExpr.y"   "t.y"         "P.Value.y"  
#[16] "adj.P.Val.y" "B.y"         "ENTREZID"    "GENENAME"   
#Current column label format:
#•	logFC.x → protein logFC 
#•	logFC.y → RNA logFC

# 2.2. Standarize naming (column labels)
ec_multi <- ec_multi %>%
  dplyr::rename(
    logFC_protein = LOGFC,
    logFC_rna     = logFC
  )

hip_multi <- hip_multi %>%
  dplyr::rename(
    logFC_protein = logFC.x,
    logFC_rna     = logFC.y

# QC check - Confirm alignment
colnames(ec_multi)

colnames(hip_multi)

# 2.3. Perform concordance classification

ec_multi$status <- ifelse(
  sign(ec_multi$logFC_rna) == sign(ec_multi$logFC_protein),
  "Concordant",
  "Discordant"
)

hip_multi$status <- ifelse(
  sign(hip_multi$logFC_rna) == sign(hip_multi$logFC_protein),
  "Concordant",
  "Discordant"
)

# QC check 

table(ec_multi$status)
#Concordant Discordant 
#       191         95

table(hip_multi$status)
#Concordant Discordant 
#       28         24

# 2.4. Save merged datasets
#RDS files
saveRDS(ec_multi, file = "ec_multi.rds")

saveRDS(hip_multi, file = "hip_multi.rds")

#To reload later
ec_multi <- readRDS("ec_multi.rds")
hip_multi <- readRDS("hip_multi.rds")

#CSV files
write.csv(ec_multi, "ec_multi.csv", row.names = FALSE)
write.csv(hip_multi, "hip_multi.csv", row.names = FALSE)

# An additional QC check before visualizations
dim(ec_multi)
#[1] 286  20

dim(hip_multi)
#[1] 52 20

head(ec_multi$SYMBOL)
#[1] "SGTB"     "APCS"     "MAOB"     "GJA1"     "SELENBP1" "ORM1"    

head(hip_multi$SYMBOL)
#[1] "HSPB6"  "S100A6" "PGAM2"  "AHNAK"  "AQP4"   "ICAM1" 

## 3. Visualizations

# 3.1. Scatter Plots

#EC scatter

library(ggplot2)

p1 <- ggplot(ec_multi, aes(logFC_rna, logFC_protein)) +
  geom_point(alpha = 0.7, size = 2) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  theme_minimal() +
  labs(title = "EC: RNA vs Protein",
       x = "RNA logFC",
       y = "Protein logFC")

#HIP scatter

p2 <- ggplot(hip_multi, aes(logFC_rna, logFC_protein)) +
  geom_point(alpha = 0.7, size = 2) +
  geom_vline(xintercept = 0, linetype = "dashed") +
  geom_hline(yintercept = 0, linetype = "dashed") +
  theme_minimal() +
  labs(title = "HIP: RNA vs Protein",
       x = "RNA logFC",
       y = "Protein logFC")

# Combine into single panel

library(gridExtra)

grid.arrange(p1, p2, ncol = 2)

# Create concordance variable (EC example)
ec_multi$concordance <- ifelse(
  sign(ec_multi$logFC_rna) == sign(ec_multi$logFC_protein),
  "Concordant",
  "Discordant"
)

#improved EC concordance plot 
library(ggplot2)

p1 <- ggplot(ec_multi, aes(
  x = logFC_rna,
  y = logFC_protein,
  color = concordance
)) +
  geom_point(size = 2.5, alpha = 0.8) +
  
  # reference lines
  geom_vline(xintercept = 0, linetype = "dashed", linewidth = 0.4) +
  geom_hline(yintercept = 0, linetype = "dashed", linewidth = 0.4) +
  
  # styling
  scale_color_manual(values = c(
    "Concordant" = "#2C7BB6",
    "Discordant" = "#D7191C"
  )) +
  
  theme_minimal(base_size = 14) +
  
  labs(
    title = "EC: AD vs Control RNA–Protein Concordance",
    x = "RNA logFC (AD vs Control)",
    y = "Protein logFC (AD vs Control)",
    color = "Concordance"

  )

#improved HIP concordance plot 
hip_multi$concordance <- ifelse(
  sign(hip_multi$logFC_rna) == sign(hip_multi$logFC_protein),
  "Concordant",
  "Discordant"
)

p2 <- ggplot(hip_multi, aes(
  x = logFC_rna,
  y = logFC_protein,
  color = concordance
)) +
  geom_point(size = 2.5, alpha = 0.8) +
  
  geom_vline(xintercept = 0, linetype = "dashed", linewidth = 0.4) +
  geom_hline(yintercept = 0, linetype = "dashed", linewidth = 0.4) +
  
  scale_color_manual(values = c(
    "Concordant" = "#2C7BB6",
    "Discordant" = "#D7191C"
  )) +
  
  theme_minimal(base_size = 14) +
  
  labs(
    title = "HIP: AD vs Control RNA–Protein Concordance",
    x = "RNA logFC (AD vs Control)",
    y = "Protein logFC (AD vs Control)",
    color = "Concordance"
  )

# combined panel
library(gridExtra)

grid.arrange(p1, p2, ncol = 2)

```{r, echo=FALSE}
# This converts your local image into a Base64 string and displays it
# No external path will be needed after the HTML is generated
img_data <- knitr::image_uri("/Users/mirandapestrofa/Downloads/MultimodalAnalysisAD/MultimodalFiles/MultimodalAnalysis_ConcordancePlots.png")
```
<img src="`r img_data`" style="width:70%; display:block; margin:auto;" />

# 2.5. Define overlapping genes

overlap_genes <- ec_multi$SYMBOL
overlap_genes

#compute correlation
r_ec <- cor(ec_multi$logFC_rna,
            ec_multi$logFC_protein,
            use = "complete.obs")

# improved EC plot with labels and correlation
library(ggplot2)
library(ggrepel)

p1 <- ggplot(ec_multi, aes(
  x = logFC_rna,
  y = logFC_protein,
  color = concordance
)) +
  
  geom_point(size = 2.5, alpha = 0.8) +
  
  # highlight zero lines
  geom_vline(xintercept = 0, linetype = "dashed", linewidth = 0.4) +
  geom_hline(yintercept = 0, linetype = "dashed", linewidth = 0.4) +

# label overlapping genes
  geom_text_repel(
    data = subset(ec_multi, SYMBOL %in% overlap_genes),
    aes(label = SYMBOL),
    size = 3,
    max.overlaps = Inf
  ) +
  
  # manual colors
  scale_color_manual(values = c(
    "Concordant" = "#2C7BB6",
    "Discordant" = "#D7191C"
  )) +
  
  theme_minimal(base_size = 14) +
  
  labs(
    title = "EC: RNA vs Protein (AD vs Control)",
    subtitle = paste0("Pearson r = ", round(r_ec, 2)),
    x = "RNA logFC (AD vs Control)",
    y = "Protein logFC (AD vs Control)",
    color = "Concordance"
  )

# improved HIP plot with labels and correlation
r_hip <- cor(hip_multi$logFC_rna,
             hip_multi$logFC_protein,
             use = "complete.obs")

p2 <- ggplot(hip_multi, aes(
  x = logFC_rna,
  y = logFC_protein,
  color = concordance
)) +
  
  geom_point(size = 2.5, alpha = 0.8) +
  
  geom_vline(xintercept = 0, linetype = "dashed", linewidth = 0.4) +
  geom_hline(yintercept = 0, linetype = "dashed", linewidth = 0.4) +
  
  geom_text_repel(
    data = subset(hip_multi, SYMBOL %in% overlap_genes),
    aes(label = SYMBOL),
    size = 3,
    max.overlaps = Inf
  ) +
  
  scale_color_manual(values = c(
    "Concordant" = "#2C7BB6",
    "Discordant" = "#D7191C"
  )) +
  
  theme_minimal(base_size = 14) +
  
  labs(
    title = "HIP: RNA vs Protein (AD vs Control)",
    subtitle = paste0("Pearson r = ", round(r_hip, 2)),
    x = "RNA logFC (AD vs Control)",
    y = "Protein logFC (AD vs Control)",
    color = "Concordance"
  )

# Combine plots into single figure
library(gridExtra)

grid.arrange(p1, p2, ncol = 2)

```{r, echo=FALSE}
# This converts your local image into a Base64 string and displays it
# No external path will be needed after the HTML is generated
img_data1 <- knitr::image_uri("/Users/mirandapestrofa/Downloads/MultimodalAnalysisAD/MultimodalFiles/MultimodalAnalysis_annotatedConcordancePlot.png")
```
<img src="`r img_data1`" style="width:70%; display:block; margin:auto;" />

## 2.6. Quadrant plot 

###The plot splits genes into 4 biological classes:
#•	↑RNA / ↑Protein (true activation) 
#•	↓RNA / ↓Protein (true repression) 
#•	↑RNA / ↓Protein (post-transcriptional repression) 
#•	↓RNA / ↑Protein (compensatory regulation) 
###

ec_multi$quadrant <- with(ec_multi,
  ifelse(logFC_rna > 0 & logFC_protein > 0, "Up-Up",
  ifelse(logFC_rna < 0 & logFC_protein < 0, "Down-Down",
  ifelse(logFC_rna > 0 & logFC_protein < 0, "RNA↑ Protein↓",
         "RNA↓ Protein↑")))
)

ggplot(ec_multi, aes(logFC_rna, logFC_protein, color = quadrant)) +
  geom_point(size = 2.5) +
  geom_vline(xintercept = 0, linetype="dashed") +
  geom_hline(yintercept = 0, linetype="dashed") +
  theme_minimal()

# EC Quadrant Plot
```{r, echo=FALSE}
# This converts your local image into a Base64 string and displays it
# No external path will be needed after the HTML is generated
img_data2 <- knitr::image_uri("/Users/mirandapestrofa/Downloads/MultimodalAnalysisAD/MultimodalFiles/Quadrant_EC_plot.png")
```
<img src="`r img_data2`" style="width:70%; display:block; margin:auto;" />


hip_multi$quadrant <- with(hip_multi,
  ifelse(logFC_rna > 0 & logFC_protein > 0, "Up-Up",
  ifelse(logFC_rna < 0 & logFC_protein < 0, "Down-Down",
  ifelse(logFC_rna > 0 & logFC_protein < 0, "RNA↑ Protein↓",
         "RNA↓ Protein↑")))
)

ggplot(hip_multi, aes(logFC_rna, logFC_protein, color = quadrant)) +
  geom_point(size = 2.5) +
  geom_vline(xintercept = 0, linetype="dashed") +
  geom_hline(yintercept = 0, linetype="dashed") +
  theme_minimal()
  
# HIP Quadrant Plot  
```{r, echo=FALSE}
# This converts your local image into a Base64 string and displays it
# No external path will be needed after the HTML is generated
img_data3 <- knitr::image_uri("/Users/mirandapestrofa/Downloads/MultimodalAnalysisAD/MultimodalFiles/Quadrant_Hip_plot.png")
```
<img src="`r img_data3`" style="width:70%; display:block; margin:auto;" />

# Density/Distribution comparison (RNA vs protein)
library(tidyr)

df_long <- ec_multi %>%
  select(logFC_rna, logFC_protein) %>%
  pivot_longer(cols = everything(),
               names_to = "type",
               values_to = "logFC")

ggplot(df_long, aes(logFC, fill = type)) +
  geom_density(alpha = 0.4) +
  theme_minimal()


library(tidyr)

df_long <- hip_multi %>%
  select(logFC_rna, logFC_protein) %>%
  pivot_longer(cols = everything(),
               names_to = "type",
               values_to = "logFC")

ggplot(df_long, aes(logFC, fill = type)) +
  geom_density(alpha = 0.4) +
  theme_minimal()


## 2.7. RNA vs Protein Regression Plot

ggplot(ec_multi, aes(logFC_rna, logFC_protein)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_minimal()
  
# EC Regression Plot
```{r, echo=FALSE}
# This converts your local image into a Base64 string and displays it
# No external path will be needed after the HTML is generated
img_data4 <- knitr::image_uri("/Users/mirandapestrofa/Downloads/MultimodalAnalysisAD/MultimodalFiles/RegressionPlot_EC.png")
```
<img src="`r img_data4`" style="width:70%; display:block; margin:auto;" /> 


ggplot(hip_multi, aes(logFC_rna, logFC_protein)) +
  geom_point() +
  geom_smooth(method = "lm") +
  theme_minimal()

# HIP Regression Plot  
```{r, echo=FALSE}
# This converts your local image into a Base64 string and displays it
# No external path will be needed after the HTML is generated
img_data5 <- knitr::image_uri("/Users/mirandapestrofa/Downloads/MultimodalAnalysisAD/MultimodalFiles/RegressionPlot_HIP.png")
```
<img src="`r img_data5`" style="width:70%; display:block; margin:auto;" />

## 2.8. Combined Quadrant and Concordance Plots

# Reload required packages
library(ggplot2)
library(dplyr)
library(ggrepel)
library(gridExtra)

# Define quadrant Categories
ec_multi$quadrant <- case_when(
  ec_multi$logFC_rna > 0 & ec_multi$logFC_protein > 0 ~ "Up-Up",
  ec_multi$logFC_rna < 0 & ec_multi$logFC_protein < 0 ~ "Down-Down",
  ec_multi$logFC_rna > 0 & ec_multi$logFC_protein < 0 ~ "RNA↑ Protein↓",
  ec_multi$logFC_rna < 0 & ec_multi$logFC_protein > 0 ~ "RNA↓ Protein↑"
)


hip_multi$quadrant <- case_when(
  hip_multi$logFC_rna > 0 & hip_multi$logFC_protein > 0 ~ "Up-Up",
  hip_multi$logFC_rna < 0 & hip_multi$logFC_protein < 0 ~ "Down-Down",
  hip_multi$logFC_rna > 0 & hip_multi$logFC_protein < 0 ~ "RNA↑ Protein↓",
  hip_multi$logFC_rna < 0 & hip_multi$logFC_protein > 0 ~ "RNA↓ Protein↑"
)

# Ensure Concordance column exists
ec_multi$concordance <- ifelse(
  sign(ec_multi$logFC_rna) == sign(ec_multi$logFC_protein),
  "Concordant",
  "Discordant"
)

hip_multi$concordance <- ifelse(
  sign(hip_multi$logFC_rna) == sign(hip_multi$logFC_protein),
  "Concordant",
  "Discordant"
)

# Create Quadrant plot with annotated gene labels
#EC plot
p1 <- ggplot(ec_multi, aes(x = logFC_rna, y = logFC_protein)) +

  # points colored by quadrant
  geom_point(aes(color = quadrant), size = 2.5, alpha = 0.85) +

  # zero reference lines
  geom_vline(xintercept = 0, linetype = "dashed", linewidth = 0.4) +
  geom_hline(yintercept = 0, linetype = "dashed", linewidth = 0.4) +

  # label ONLY your overlapping genes
  geom_text_repel(
    data = ec_multi %>% filter(!is.na(SYMBOL)),
    aes(label = ifelse(SYMBOL %in% ec_multi$SYMBOL[1:6], SYMBOL, "")),
    size = 3,
    max.overlaps = Inf,
    show.legend = FALSE
  ) +

  theme_minimal(base_size = 14) +

  labs(
    title = "EC: RNA–Protein Quadrant Structure (AD vs Control)",
    x = "RNA logFC",
    y = "Protein logFC",
    color = "Quadrant"
  )

#HIP plot
p1 <- ggplot(hip_multi, aes(x = logFC_rna, y = logFC_protein)) +

  # points colored by quadrant
  geom_point(aes(color = quadrant), size = 2.5, alpha = 0.85) +

  # zero reference lines
  geom_vline(xintercept = 0, linetype = "dashed", linewidth = 0.4) +
  geom_hline(yintercept = 0, linetype = "dashed", linewidth = 0.4) +

  # label ONLY your overlapping genes
  geom_text_repel(
    data = hip_multi %>% filter(!is.na(SYMBOL)),
    aes(label = ifelse(SYMBOL %in% ec_multi$SYMBOL[1:6], SYMBOL, "")),
    size = 3,
    max.overlaps = Inf,
    show.legend = FALSE
  ) +

  theme_minimal(base_size = 14) +

  labs(
    title = "HIP: RNA–Protein Quadrant Structure (AD vs Control)",
    x = "RNA logFC",
    y = "Protein logFC",
    color = "Quadrant"
  )

#Ensure proper labeling
overlap_genes <- ec_multi$SYMBOL

overlap_genes <- hip_multi$SYMBOL

geom_text_repel(
  data = ec_multi %>% filter(SYMBOL %in% overlap_genes),
  aes(label = SYMBOL),
  size = 3
)

geom_text_repel(
  data = hip_multi %>% filter(SYMBOL %in% overlap_genes),
  aes(label = SYMBOL),
  size = 3
)

#Create Concordance Bar Plot
#EC plot
p2 <- ggplot(ec_multi, aes(x = concordance)) +
  geom_bar(fill = "steelblue") +
  theme_minimal(base_size = 14) +
  labs(
    title = "EC RNA–Protein Concordance",
    x = "",
    y = "Gene count"
  )

#HIP plot
p2 <- ggplot(hip_multi, aes(x = concordance)) +
  geom_bar(fill = "steelblue") +
  theme_minimal(base_size = 14) +
  labs(
    title = "HIP RNA–Protein Concordance",
    x = "",
    y = "Gene count"
  )

#Combine into one figure
grid.arrange(p1, p2, ncol = 2)


#EC combined plot
```{r, echo=FALSE}
# This converts your local image into a Base64 string and displays it
# No external path will be needed after the HTML is generated
img_data6 <- knitr::image_uri("/Users/mirandapestrofa/Downloads/MultimodalAnalysisAD/MultimodalFiles/CombinedECplot_QUADandConcor.png")
```
<img src="`r img_data6`" style="width:70%; display:block; margin:auto;" />

#HIP combined plot
```{r, echo=FALSE}
# This converts your local image into a Base64 string and displays it
# No external path will be needed after the HTML is generated
img_data7 <- knitr::image_uri("/Users/mirandapestrofa/Downloads/MultimodalAnalysisAD/MultimodalFiles/CombinedHIPplot_QUADandConcor.png")
```
<img src="`r img_data7`" style="width:70%; display:block; margin:auto;" />
